---
title: "Setup Infomap Fanmod executables"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setup Infomap Fanmod executables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In order to run multilayer community detection, we will need the Infomap (old version). The source can be downloaded from [mapequation.org](https://www.mapequation.org/code_old.html#Installation), where you can find also the installation (download and compile) guidelines.

Once you compiled the code, save the `path/to/Infomap` in the `infomap-setup` chunk in the vignettes or into your code/notebook.

In the `src/` folder there is already the linux executable for the Infomap. See [Multilayer community detection](/docs/articles/ml_community.html) for the vignette.

```{r infomap-setup, eval = FALSE}
pathInfomap <- "path/to/Infomap"
# or
pathInfomap <- "src/infomap-0.x/Infomap"
```

The same applies for the multilayer network motifs: the executables for fanmod (downloaded from [here](https://github.com/gtremper/Network-Motif/tree/master/fanmod)) are already placed in the `src/` folder. See [Multilayer network motifs](./docs/articles/ml_motifs.html)  for the vignette.

```{r fanmod-setup, eval = FALSE}
pathFanmod <- "path/to/fanmod"
# or
pathFanmod <- "../src/fanmod_linux"
```

#### References

Manlio De Domenico, Andrea Lancichinetti, Alex Arenas, and Martin Rosvall, Physical Review X 5, 011027 (2015) [doi: 10.1103/PhysRevX.5.011027](https://doi.org/10.1103/PhysRevX.5.011027)
[Source: mapequation.org](http://www.mapequation.org/code.html)

Sebastian Wernicke and Florian Rasche, Bioinformatics 22, 1152 (2006)
Version implemented by Tomer Benyamini, Yoav Teboulle, Tel-Aviv University
[github/gtremper/Network-Motif](https://github.com/gtremper/Network-Motif/tree/master/fanmod/FANMOD-command_line-source)
